Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-01-24 ms.tex
I added an MCMC fit to 2MASS 1821 in addition to the one yesterday for 2MASS 0835.
I plotted the results of an experiment where I scaled all the error bars up by a factor of 4X.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{mcmc_spectrum_2mass_0835.pdf}
\caption{Spectrum of \sha\ using all MCMC fits with 1 cosine term .}\label{fig:mcmcSpec0835}
\end{centering}
\end{figure}

>>>>

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835 - Manual Shifting]{
	\includegraphics[width=0.5\textwidth]{mcmc_spectrum_2mass_0835.pdf}
	\label{fig:ampSpec0835ManualS}
	}
\subfloat[2MASS J1821 - Manual shifting ]{
	\includegraphics[width=0.5\textwidth]{mcmc_spectrum_2mass_1821.pdf}
	\label{fig:ampSpec1821ManualS}
	}
	\caption{Amplitude spectrum of {\sha} (left)  and {\shb} (right) using manual wavelength shifting, 1 cosine term fit and MCMC fitting with error bars from photon and read noise.}
	\label{fig:ampSpecManualS}
	\vspace{0.1in}
\end{figure*}

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835 - 4$\times \sigma$]{
	\includegraphics[width=0.5\textwidth]{mcmc_2mass_0835_spectrum_0400perc_err.pdf}
	\label{fig:ampSpec0835fourTimesErr}
	}
\subfloat[2MASS J1821 - 4$\times \sigma$ ]{
	\includegraphics[width=0.5\textwidth]{mcmc_2mass_1821_spectrum_0400perc_err.pdf}
	\label{fig:ampSpec1821fourTimesErr}
	}
	\caption{As an experiment, I remade the amplitude spectra of Figure \ref{fig:ampSpecManualS} but scaled all error bars up by a factor of 4 for all points to account for some systematic errors. IE, Amplitude spectrum of {\sha} (left)  and {\shb} (right) using manual wavelength shifting, 1 cosine term fit and MCMC fitting with error bars from 4$\times$ photon and read noise.}
	\label{fig:ampSpecManualSfourTimesErr}
	\vspace{0.1in}
\end{figure*}
